### 2016-02-08 prepReport/theorBack.tex
Corrected reference error
Finished Teoretical Part. Started State-of-the-art. Cleaned up uncessary inital chaps

\begin{figure}[!H]
	\begin{subfigure}{0.5\linewidth}
		\centering
		\includegraphics[width=0.9\linewidth]{figures/neuron.eps}
		\caption{Neural Network Node}
		\label{fig:modelNeuron_a}
	\end{subfigure}
	\begin{subfigure}{0.5\linewidth}
		\centering
		\includegraphics[width=0.9\linewidth]{figures/multipolarNeuron.png}
		\caption{Biological Neuron Diagram}
		\label{fig:modelNeuron_b}
	\end{subfigure}

	\caption{In Figure~\ref{fig:modelNeuron_a}. each input feature $x_i$ is weighted by its corresponding weight $w_i$. During the training procedure, these weights are adjusted so that the output $y$ approaches the target value. In Figure~\ref{fig:modelNeuron_b}, we see the diagram of an actual multi polar neuron. The dendrites, where the stimuli are received, plays a role similar to that of the input nodes. The axon transmits the signal to the synaptic terminals, that are similar to the $y$ output}
	\label{fig:modelNeuron}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\linewidth]{figures/lstmneuron.png}
    \caption{A complete LSTM neuron, with all the features as described in~\cite{Graves05}}
	\label{fig:lstmneuron}
\end{figure}

@@

>>>>

\begin{figure}[H]
	\begin{subfigure}{0.5\linewidth}
		\centering
		\includegraphics[width=0.9\linewidth]{figures/neuron.eps}
		\caption{Neural Network Node}
		\label{fig:modelNeuron_a}
	\end{subfigure}
	\begin{subfigure}{0.5\linewidth}
		\centering
		\includegraphics[width=0.9\linewidth]{figures/MultipolarNeuron.png}
		\caption{Biological Neuron Diagram}
		\label{fig:modelNeuron_b}
	\end{subfigure}

    \caption{In Figure~\ref{fig:modelNeuron_a}. each input feature $x_i$ is weighted by its corresponding weight $w_i$. During the training procedure, these weights are adjusted so that the output $y$ approaches the target value. In Figure~\ref{fig:modelNeuron_b}, we see the diagram of an actual multi polar neuron. The dendrites, where the stimuli are received, plays a role similar to that of the input nodes. The axon transmits the signal to the synaptic terminals, that are similar to the $y$ output. Source: \href{https://en.wikipedia.org/wiki/Neuron\#/media/File:Neuron\_Hand-tuned.sv://en.wikipedia.org/wiki/Neuron\#/media/File:Blausen\_0657\_MultipolarNeuron.png}{Wikipedia}}
	\label{fig:modelNeuron}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\linewidth]{figures/lstmneuron.png}
    \caption{A complete LSTM neuron, with all the features as described in~\cite{Graves05}. Source:~\cite{Greff15}}
	\label{fig:lstmneuron}
\end{figure}

@@

\section{Proposed Solution}\label{sec:propSol}
Given the previous discusson of how LSTM neurons work, their benefits when compared to other RNN architectures, this work aims to conceive an efficient dedicated FPGA implementation with on-chip learning that, hopefully, surpasses the training/testing time of an equivalent CPU implementation in a general high-level language or from a framework.

As discussed in Chapter~\ref{chap:stateArt}, hitherto there is only one FPGA implementation of LSTM cells~\cite{Chang15}, but there is no on-chip learning on the architecture (the weights are learned offline, and loaded in the FPGA before operation, and they are not changed while the FPGA system is operating), and my proposed work will implement an efficient LSTM implementation \emph{with} the ability to learn on-chip, which is an innovative and useful feature for the LSTM architecture on a dedicated hardware implementation. I will achieve that using the SPSA method described in~\ref{sec:training_lstm}, and inspired in the previous work of~\cite{Maeda05}.

This solution will combine the benefits of a dedicated hardware implementation, where the inherent parallelism so obviously visible in the network architecture can be fully exploited something that, predominantly, yields a much higher performance in terms of computation time than a naïve CPU implementation, as in~\cite{Maeda05} where a $21\times$ speed-up against an ARM CPU was acheived.
